How Important are Usage Examples in REST API Documentation?

### 2017-03-06 controlled_study.tex
skeleton graph added

\ifCLASSINFOpdf
  \usepackage{listings}
  \usepackage[pdftex]{graphicx}
  \usepackage{url}

@@

A graph showing the difference in productivity metrics between G1 and G2.
Implications

>>>>

\ifCLASSINFOpdf
  \usepackage{listings}
  \usepackage[pdftex]{graphicx}
  \usepackage{url}
  \usepackage{tikz,pgfplots,pgfplotstable}
  \usepgfplotslibrary{statistics}

@@

\pgfplotsset{compat=1.14}
\usetikzlibrary{patterns}
\pgfplotstableread[col sep=comma]{groupone.csv}\groupone

\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Trial API Calls,
        title=Comparison of Trial vs. Successful API Calls,
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {groupone.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {grouptwo.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

    \begin{axis}[
      axis y line*=right,
      axis x line=none,
      ymin=0, ymax=100,
      ylabel= Success Rate,
      yticklabel={\pgfmathparse{\tick}\pgfmathprintnumber{\pgfmathresult}\%},
      width=2.8in
    ]
    \addplot[dashed,mark=*,gray]
      coordinates{
        (0,0)
        (0.0148,48)
        (0.0295,66)
        (0.0441,66)
        (0.059,45.0)
    }; \addlegendentry{G1 Success Rate}

    \addplot[smooth,mark=*,black]
      coordinates{
        (0,0)
        (0.0148,20)
        (0.0295,10)
        (0.0441,6)
        (0.059,5.0)
    }; \addlegendentry{G2 Success Rate}
    \end{axis}

\end{tikzpicture}
